Estimating individual subjective values of emotion regulation strategies

### 2023-02-13 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.tex
knitted document

The authors made the following contributions. Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Writing - review \& editing. \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.

@@

@@

\caption{\label{tab:unnamed-chunk-3}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distancing$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
$View_{negative} - Distraction$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}

>>>>

The authors made the following contributions. Christoph Scheffel: Conceptualization, Methodology, Funding acquisition, Formal analysis, Investigation, Project administration, Software, Visualization, Writing - original draft preparation, Writing - review \& editing; Josephine Zerna: Conceptualization, Methodology, Funding acquisition, Investigation, Project administration, Software, Visualization, Writing - review \& editing; Anne Gärtner: Formal analysis, Writing - review \& editing; Denise Dörfel: Conceptuatlization, Writing - review \& editing; Alexander Strobel: Conceptualization, Methodology, Writing - review \& editing. \textsuperscript{$\dagger{}$} Christoph Scheffel and Josephine Zerna contributed equally to this work.

@@

\hypertarget{results}{%
\section{3. Results}\label{results}}

\hypertarget{participants-and-descriptive-statistics}{%
\subsection{3.1 Participants and descriptive statistics}\label{participants-and-descriptive-statistics}}

Data collection took place between 2022-08-16 and 2023-02-03.

\hypertarget{confirmatory-analyses}{%
\subsection{3.2. Confirmatory analyses}\label{confirmatory-analyses}}

\hypertarget{exploratory-analyses}{%
\subsection{3.3. Exploratory analyses}\label{exploratory-analyses}}

@@

\caption{\label{tab:unnamed-chunk-4}Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-5}Paired contrasts for the rmANOVA comparing subjective arousal of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-6}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-7}Paired contrasts for the rmANOVA comparing physiological responding (Levator activity) of negative and neutral pictures in the condition "active viewing".}

@@

\caption{\label{tab:unnamed-chunk-8}Paired contrasts for the rmANOVA comparing physiological responding (Corrugator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-9}Paired contrasts for the rmANOVA comparing physiological respodning (Levator activity) of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

@@

\caption{\label{tab:unnamed-chunk-10}Paired contrasts for the rmANOVA comparing subjective effort of conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression".}

\begin{tabular}{lllllllll}
\toprule
Contrast & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{$SE$} & \multicolumn{1}{c}{$df$} & \multicolumn{1}{c}{$t$} & \multicolumn{1}{c}{$p$} & \multicolumn{1}{c}{$BF10$} & \multicolumn{1}{c}{$\eta_{p}^{2}$} & \multicolumn{1}{c}{$95\% CI$}\\
\midrule
$View_{negative} - Distraction$ & -110.72 & 20.85 & 45.00 & -5.31 & 0.00 & 59.77 & 0.39 & {}[0.20, 1.00]\\
$View_{negative} - Distancing$ & -89.72 & 20.85 & 45.00 & -4.30 & 0.00 & 20.49 & 0.29 & {}[0.12, 1.00]\\
$View_{negative} - Suppression$ & -88.15 & 20.85 & 45.00 & -4.23 & 0.00 & 33.13 & 0.28 & {}[0.11, 1.00]\\
$Distraction - Distancing$ & 21.00 & 20.85 & 45.00 & 1.01 & 1.00 & 0.50 & 0.02 & {}[0.00, 1.00]\\
$Distraction - Suppression$ & 22.57 & 20.85 & 45.00 & 1.08 & 1.00 & 0.57 & 0.03 & {}[0.00, 1.00]\\
$Distancing - Suppression$ & 1.57 & 20.85 & 45.00 & 0.08 & 1.00 & 0.26 & 1.27e-04 & {}[0.00, 1.00]\\
\bottomrule
\addlinespace
\end{tabular}
